---
title: "Asignment 3 Gurung"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
library(reshape2)
library(maps)
library(ggplot2)
library(knitr)
source("analysis.R")


knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

<p>For my own interests and because I am a representative of Asian Americans and Pacific Islanders group I decided to focus on them for this assignment. I wondered how the number of incarcerations of AAPI members who are considered the *model minority* would be in a place like Washington where there are counties full of Asian Americans and Pacific Islanders. The variable I chose to focus on was aapi_pop_15to64</p>

<p> To explore this variable which stood for the population of Asian Americans and Pacific Islanders in incarceration I found it helpful to have the total population of incarcerations. This let me calculate multiple values that could help me understand the data better. First I was able to find the average number of WA AAPI incarcerations by county in 2018 (14795) and 1990 (3641). I also found the ratios of AAPI incarcerations to Total population in 2018 (11.6%) compared to 1990 (4.4%). Lastly I found the highest number of incarcerations was in King County which isn't surprising but the number was well above what I expected as it was **340132** in 2018!<p>

## Charts

```{r chart1, echo=FALSE}
aapiVstotalWA <- ggplot(yearly_dataWA,aes(x = year, y = Population))+
  geom_line(aes(color= Aapi_vs_total))+
  scale_color_manual(values = c("red", "blue"))+
  labs(title = "Total AAPI vs Total Population in WA over time", color="Different Populations")
aapiVstotalWA
```
```{r chart2, echo=FALSE}
aapiWA <- ggplot(data_aapi,aes(x = total_pop_15to64, y = aapi_pop_15to64))+
  geom_point()+
  labs(title = "AAPI vs Population")
aapiWA

aapiWAver2 <- ggplot(data_aapiver2,aes(x = total_pop_15to64, y = aapi_pop_15to64))+
  geom_point()+
  labs(title = "AAPI vs Population in WA Version 2")+
  xlim(0,200000)+
  ylim(0,20000)
aapiWAver2
```
```{r map, echo=FALSE}
#this code was from my TA! she showed us how to make the map look a bit better.
blank_theme <- theme_bw() +
  theme(
    axis.line = element_blank(), # remove axis lines
    axis.text = element_blank(), # remove axis labels
    axis.ticks = element_blank(), # remove axis ticks
    axis.title = element_blank(), # remove axis titles
    plot.background = element_blank(), # remove gray background
    panel.grid.major = element_blank(), # remove major grid lines
    panel.grid.minor = element_blank(), # remove minor grid lines
    panel.border = element_blank() # remove border around plot
  )

aapiWA_map <- ggplot(map_data) + 
  geom_polygon(
    mapping = aes(x = long, y = lat, group = group, fill = aapi_pop_15to64),
    color="grey", size = .5
  ) + 
  coord_map() + 
  scale_fill_continuous(limits = c(0, max(map_data$aapi_pop_15to64)),low="white", high="blue") + 
  blank_theme +
  ggtitle("AAPI incarcerations WA 2018")
aapiWA_map


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
